\documentclass[acmtog, authorversion]{acmart}

\usepackage{booktabs} % For formal tables

% TOG prefers author-name bib system with square brackets
\citestyle{acmauthoryear}
\setcitestyle{square}


\usepackage[ruled]{algorithm2e} % For algorithms
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

% Metadata Information
\acmJournal{TOG}
\acmVolume{9}
\acmNumber{4}
\acmArticle{39}
\acmYear{2018}
\acmMonth{4}

% Copyright
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\acmDOI{0000001.0000001_2}

% Paper history
\received{January 2018}
\received{March 2018}
\received[final version]{April 2018}
\received[accepted]{April 2018}


% Document starts
\begin{document}
% Title portion
\title{Virtualization and The Cloud Ecosystem : A Brief Survey Paper}

\author{Rajvi Tiwari}
\orcid{1234-5678-9012-3456}
\affiliation{%
  \institution{University of Texas at Arlington}
  \streetaddress{587 Spaniolo Dr}
  \city{Arlington}
  \state{TX}
  \postcode{456010}
  \country{USA}}
\email{rajvi.tiwari@mavs.uta.edu}

\renewcommand\shortauthors{Tiwari, R. et al}

\begin{abstract}
Virtualization and virtual machine technologies are ideas 
that have gained a significant interest boom in the past 10 years. 
However, the idea is old, dating back to the 1960s. The main idea
is that a VMM (Virtual Machine Monitor) creates the illusion of 
multiple (virtual) machines on the same physical hardware. A VMM
is also known as a hypervisor. Many of the benefits of virtualized 
systems depend on the decoupling of a VM's logical I/O devices from its physical implementation. 
Examples range from the ability to multiplex many VMs on the same 
hardware to advanced virtualization features such as live migration 
and enhanced security. Virtualization is a very fundamental technology that lies at the
heart of the operations of modern Cloud Computing Infrastructure. This
technology is important to cloud computing because it provides the 
abstraction that cloud computing enjoys by taking a physical resource 
such as a server and dividing it into virtual resources called virtual
machines (multiple subscribers). This paper aims to:
1) review the existing virtualization techniques, including process 
virtualization, OS virtualization and system virtualization; 2) discuss challenges in virtualizing different types of resources, such as CPU, memory and I/O devices; 3) discuss why virtualization is the enabling technology for today's cloud ecosystem.
\end{abstract}


%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer Organization and Architecture~Multi-Thread Programing</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer Organization and Architecture~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer Organization and Architecture~Memory Management</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Computer resources~I/O and File Systems</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer Organization and Architecture~Multi-Thread Programing}
\ccsdesc[300]{Computer Organization and Architecture~Redundancy}
\ccsdesc{Computer Organization and Architecture~Memory Management}
\ccsdesc[100]{Computer resources~I/O and File Systems}

%
% End generated code
%


\keywords{virtual machine, hypervisor,
operating system, page replacement algorithms, file systems}



\maketitle

\input{samplebody-journals}



\end{document}
